Closed-loop Neuromorphic Benchmarks

### 2015-11-13 paper/paper.tex
Clarified stats

All three hardware systems drastically improve performance on this task, as
compared to the non-adaptive controller.  Statistical significance was
measured with a two-tailed t-test.

@@

Given the above considerations, the benchmark indicates that the CPU can run 23 neurons per 0.1W,
the GPU 38 neurons per 0.1W, and SpiNNaker can run 500 neurons per 0.1W.  
As shown in Figure \ref{fig:analysis_power}, the neuromorphic hardware
outperforms the CPU and GPU on this task.

@@

One more complex robotic task where this approach might be applicable is
navigation and obstacle avoidance.  Here, we would need both a more complex
minimal simulation for the environment, and an explicit neuromorphic
algorithm capable of performing this avoidance.  The minimal simulation itself
would need to include some sort of sensory modality (vision,
range sensing, or both), and movement in a two-dimensional environment
(probably wheeled movement, for simplicity).  To run such a simulation in
real-time, we would use many of the same tricks and simplifications used
in Jakobi's original work (\citealt{Jakobi97evolutionaryrobotics}).  These
included making separate simulations for corridors and intersections (rather
than generic simulations for any possible geometries), using noisy lookup
tables (rather than detailed physics simulations), treating collisions as
failures (rather than modelling them), and using shifting random dot patterns
for visual stimuli (rather than high-fidelity image rendering).  Given
Jakobi's success at building high-speed simulations over 20 years ago, we
believe real-time simulations of this type are feasible now.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_basic}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_basic} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems.
     Each system is running 500 neurons.  The hardware do not statistically
     significantly differ, but are all statistically significant improvements 
     over no adaptation ($p<0.05$).
     Scatterplots show individual runs (with random jitter on the x-axis
     to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_compute}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_compute} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of in real time.  Scatterplots show individual runs (with random
     jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  In this case,
 there is no statistical difference between the three hardware systems ($p>0.05$).}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_power}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_power} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of per 0.1 Watt of power consumption.  Scatterplots show individual runs (with random jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  The SpiNNaker system is a statistically
 significant improvement over the other two ($p<0.05$).}
\end{figure}

>>>>

All three hardware systems drastically improve performance on this task, as
compared to the non-adaptive controller.

@@

Given the above considerations, the benchmark indicates that the CPU can run 23 neurons per 0.1W,
the GPU 38 neurons per 0.1W, and SpiNNaker can run 500 neurons per 0.1W.  
As shown in Figure \ref{fig:analysis_power}, while the GPU outperforms
the CPU on this task, the neuromorphic hardware outperforms both of them.

@@

One more complex robotic task where this approach might be applicable is
navigation and obstacle avoidance.  Here, we would need both a more complex
minimal simulation for the environment, and an explicit neuromorphic
algorithm capable of performing this avoidance.  The minimal simulation itself
would need to include some sort of sensory modality (vision,
range sensing, or both), and movement in a two-dimensional environment
(probably wheeled movement, for simplicity).  To run such a simulation in
real-time, we would use many of the same optimizations and simplifications used
in Jakobi's original work (\citealt{Jakobi97evolutionaryrobotics}).  These
included making separate simulations for corridors and intersections (rather
than generic simulations for any possible geometries), using noisy lookup
tables (rather than detailed physics simulations), treating collisions as
failures (rather than modelling them), and using shifting random dot patterns
for visual stimuli (rather than high-fidelity image rendering).  Given
Jakobi's success at building high-speed simulations over 20 years ago, we
believe real-time simulations of this type are feasible now.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_basic}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_basic} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems.
     Each system is running 500 neurons.  The hardware do not statistically
     significantly differ, but are all statistically significant improvements 
     over no adaptation ($p<0.05$; two-tailed t-test with Bonferroni correction; 400 samples per condition).
     Scatterplots show individual runs (with random jitter on the x-axis
     to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_compute}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_compute} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of in real time.  Scatterplots show individual runs (with random
     jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  In this case,
 there is no statistical difference between the three hardware systems ($p>0.05$; two-tailed t-test with Bonferroni correction; 400 samples per condition).}
\end{figure}

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/plot_power}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:analysis_power} Figure \arabic{figure}.}{ Benchmark results comparing three hardware systems
     in terms of their performance when running as many neurons as they are capable of per 0.1 Watt of power consumption.  Scatterplots show individual runs (with random jitter on the x-axis to avoid overlap), the 
     shaded area is the mean plus or minus the standard deviation, and the 95\% confidence interval of the mean is shown.  
 All differences are statistically significant ($p<0.05$; two-tailed t-test with Bonferroni correction; 400 samples per condition).}
\end{figure}
